Spatial Reasoning and Statistical Graphics

### 2014-10-11 Paper/Draft1/TestingVisualAptitude.Rnw
Removing warning/error message

<<VisReasoningAnalysis,echo=FALSE, include=FALSE, fig.width=8,fig.height=8, out.width='0.9\\textwidth'>>=
lineup.summary$variable <- factor(lineup.summary$variable, labels=c("Card Rotation", "Figure Classification", "Paper Folding", "Visual Search"))

@@

<<correlations, fig.cap="Scree plot of principle component analysis of performance on the different test batteries.", out.width=".5\\linewidth", fig.height=4.5, fig.width=7.5, comment="|">>=
cor(ans.summary[,c("lineup","card_rot", "fig_class", "folding", "vis_search")])
# using scaled version right now, should be changed to unscaled once the scores are internally scaled.
pca <- prcomp(ans.summary[,c("lineup", "card_rot", "fig_class", "folding", "vis_search")], scale=T)
summary(pca)
screeplot(pca)
@

>>>>

<<VisReasoningAnalysis,echo=FALSE, include=FALSE, fig.width=8,fig.height=8, out.width='0.9\\textwidth', message=F, warning=F>>=
lineup.summary$variable <- factor(lineup.summary$variable, labels=c("Card Rotation", "Figure Classification", "Paper Folding", "Visual Search"))

@@

<<correlations, fig.cap="Scree plot of principle component analysis of performance on the different test batteries.", out.width=".5\\linewidth", fig.height=4.5, fig.width=7.5, comment="|", warning=F, message=F>>=
cor(ans.summary[,c("lineup","card_rot", "fig_class", "folding", "vis_search")])
# using scaled version right now, should be changed to unscaled once the scores are internally scaled.
pca <- prcomp(ans.summary[,c("lineup", "card_rot", "fig_class", "folding", "vis_search")], scale=T)
summary(pca)
screeplot(pca)
@
